Depression and suicidality as costly signals of need

### 2021-05-03 Paper.rmd
Added detail to vignette descriptions

Participants in the US sample were randomly assigned to either the "basketball coach," "romantic partner," or "brother-in-law" vignettes. In the "basketball coach" scenario, the star player on a university basketball team comes to the participant (who is asked to imagine themselves as the athletic director at a university) and claims she was sexually assaulted by her coach. However, there are indications the player might be lying to get more playing time.

The "brother-in-law" vignette involved participants imagining that they let their sister, brother-in-law, and niece move in with the participant and their 15-year-old daughter after their sister's family lost their house in a fire. During this time, the participant's daughter becomes jealous of her cousin before accusing her uncle of sexually assaulting her.

The "romantic partner" vignette had participants imagine that they found a highly desirable partner after years of being single. However, their 13-year-old daughter, who has a history of trying to get in the way of their relationships, is clearly not happy with this. After a period of sustained conflict, she accuses the romantic partner of physically assaulting her but cannot produce any evidence.

>>>>

Participants in the US sample were randomly assigned to either the "basketball coach," "romantic partner," or "brother-in-law" vignettes. In the "basketball coach" scenario, the star player on a university basketball team comes to the participant, who is asked to imagine themselves as the athletic director at a university, and claims she was sexually assaulted by her head coach, a physically powerful man. However, there has been a history of conflict between the star player and the coach over playing time, and police are unable to find evidence that corroborate her claims.

The "brother-in-law" vignette involved participants imagining that they let their sister, brother-in-law, and niece move in with the participant and their 15-year-old daughter after their sister's family lost their house in a fire. During this time, the participant's daughter becomes jealous of her cousin, who appears to be a social competitor. A few weeks after claiming her cousin was trying to still her boyfriend, she then accuses her uncle of sexually assaulting her.

The "romantic partner" vignette had participants imagine that they found a highly desirable partner after years of being single. However, their 13-year-old daughter, who has a history of trying to get in the way of their relationships, is clearly not happy with this. After a period of sustained conflict with both the participants and the romantic partner, she accuses the romantic partner of physically assaulting her but cannot produce any evidence.
